---
output: github_document
---

# 2020 Presidential Election Returns from Decision Desk

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="figures/")
```

## Overview

[Decision Desk HQ](https://decisiondeskhq.com) tweeted out election returns for the 2020 presidential election on the night of the election and the days that followed from [their Twittter account](https://twitter.com/DecisionDeskHQ). 

This repo preserves [those tweets](protected/decision-desk-timeline.csv) and wrangles the information into [returns](returns.csv) by time, state, and candidate.

---

## Details

- `01-get-tweets.R` downloads and saves Decision Desk HQ's Twitter timeline, which contains important tweets with the vote counts at particular point in time for important states. This scripts writes the raw timeline as `raw/decision-desk-timeline.rds` and a slightly altered version as `raw/decision-desk-timeline.csv`.
- `02-wrangle-tweets.R` takes the raw tweets from `protected/` (not `raw/`, see note below) and extracts the relevant information. It saves the data as `returns.rds` and `returns.csv`. Because of the `dttm` objects, RDS works a bit better here.

The scripts do not automatically write to the `protected/` directory. I create this directory by manually copying the `raw/` directory. This protects against accidentally deleting the raw tweets that contain the relevant information.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)

returns <- read_rds("returns.rds") %>%
  glimpse()
```

---

## Read Directly from Web

You can read the RDS data directly from GitHub with `rio::import()`.

```{r}
r <- rio::import("https://github.com/carlislerainey/decision-desk-hq-returns/raw/master/returns.rds") 
```

## GA Returns Example

```{r ga}
ga <- returns %>%
  filter(state == "GA") %>%
  filter(time > ymd("2020-11-05"))

ggplot(ga, aes(x = time, y = votes, color = candidate)) + 
  geom_line() + 
  scale_y_log10() + 
  scale_color_manual(values = c("Biden" = scales::muted("blue"),
                                "Trump" = scales::muted("red"))) + 
  labs(title = "Presidental Election Returns in GA") + 
  theme_bw()
```

